---
title: "Exercise 1B"
format: html
editor: visual
---


## Clearing Rs memory
We will start by clearing Rs memory
```{r}
rm(list = ls())
```

##Aim
We want to create an executable HTML document that samples
100 values from a log-normal distribution (see the rlnorm function

##Loading libraries
Here we load the necessary libraries
```{r}
library(ggplot2)
library(tidyverse)
library(palmerpenguins)
library(quarto)
``` 

##creating the data
here we create the dataset we will be using
```{r}

set.seed(1234)

data1 <- rlnorm(n = 100, mean = 5, sd = 0.5)

data=data.frame(value=data1)

head(data1)

```

## Plots
In this section we will create the plots requested

### Histogram
First the histogram with the linear scale
```{r}
linearhistogram <- ggplot(data, aes(x=value)) +
  geom_histogram(bins = 100) 
linearhistogram
```
##log scale histogram
Next the histogram with the logarithmic scale
```{r}
loghist <- ggplot(data, aes(log(x=value))) +
  geom_histogram(bins = 100) 
loghist
```

##Violin plot
Here we create a violin plot

```{r}
data$log_value <- log(data$value)

violoinplot <- ggplot(data, aes(x = value, y = log_value)) +
  geom_violin() +
   labs(y = "Log-Transformed Value") +
  ggtitle("Violin Plot")
violoinplot

```

##Next comes the statistical analysis
Here we will do the statistical analysis and embed it in the text
```{r}
mean(data1)

```
The mean of our distribution is
`r mean(data1)`

### Standard deviation

Here we will do the statistical analysis and embed it in the text

```{r}
sd(data1)

```

The standard deviation of our distribution is `r sd(data1)`



